---
title       : Diamond Pricing
subtitle    : Shiny app for diamond reference
author      : Terence G
job         : Data Scientist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : standalone # {standalone, draft}
knit        : slidify::knit2slides
---

## Diamond Pricing application

Accessible via https://fat2301.shinyapps.io/shiny_project_diamond_price/  
Source code at https://github.com/fat2301/dataproducts.git  
  
___Description___ This application provides useful information about a diamond's 4C attributes. It allows the user to input the 4Cs of a diamond, and get basic information based on that input, including a reference price.  



--- .class #id 

## Key Features

1. Cross-references the diamond attributes in real-time to a statistical model generated from R's ggplot2 diamonds library to come up with a price reference. Updates as attributes are changed!
2. Provides educational information such as what clarity and colors mean. 
3. Really simple and easy to use.

--- 


## Key Features continued - Histogram comparison

```{r echo=FALSE}
library(ggplot2)

```


```{r}
carat <- 1.25; #If carat slider is set to 1.25, it will overlay on histogram of diamond dataset.
```


```{r echo=FALSE}
hist(diamonds$carat, breaks = 20, xlim= c(0,2.5), col = 'darkgray', border = 'white',
         main = "How common is your diamond size?",xlab = "Carat Size", ylab = "Number of diamonds for that size") ; 

abline(v=carat,col="red")
```


--- 


## Acknowledgements and Disclaimers

Reference information about the 4Cs from:  
 http://www.4cs.gia.edu/en-us/the-diamond-4-cs.htm  
 
Disclaimer: This app is only intended to try out the Shiny feature of R for the Coursera course in Developing Data Products. Minimal effort was taken in building the pricing model and should not be taken seriously.  

